---
title: "Overview of the farspackage"
author: "Leo Eskin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The farspackage is a collection of simple functions that read, summarize and/or map data from 
the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (fars).  

Each of the farspackage functions requires that the fars database files be present in the current working
directory, so the user should use setwd() as necessary to set the current directory to the location
of the data files before calling the farspackage function(s).

To read one or more years of data from the fars database and store the results in data frame format, 
the fars_read_years() function may be used.  This example reads the accident results for 2013
and 2015 into the fars_2013_2015 data frame (and then displays the data frame):

```{r}
library(farspackage)
fars_2013_2015 <- fars_summarize_years(c("2013","2015"))
fars_2013_2015
```

The fars_summarize_years creates a column in the data frame for each desired year, and a row for each month.  The total number
of fatal accidents for each month is reported.

To plot a map of fatality data for one state from the fars database for a given year, 
the fars_map_state() function may be used.  This example reads and plots on a map, each of the fatal accidents for 2013 
for the state of Alabama (state number 1).

```{r}
library(farspackage)
library(maps)
fars_map_state("1","2013")
```


